Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-25 doc/RMD/mlg-mcg.Rmd
update manuscript and calculation of singletons

mcg_mlg_graph
ggsave(plot = mcg_mlg_graph, filename = file.path(PROJHOME, "results/figures/publication/FigureS2.pdf"), 
       width = 88*3, height = 88*3.5, units = "mm")
```

Of interest is accounting for the communities that have a single MCG/MLG pair.
We can detect these by filtering for communities that only have two members:

```{r}
singles <- the_communities %>% 
  count(community) %>% 
  arrange(desc(n)) %>% 
  filter(n == 2) %>% 
  inner_join(the_communities, by = "community") %>% 
  mutate(type = case_when(grepl("MLG", vertex) ~ "MLG", TRUE ~ "MCG")) %>% 
  spread(type, vertex) %>%
  select(-n, -comm)
# assessing that this truely contains the singletons
nrow(inner_join(singles, the_communities, by = c("MCG" = "vertex")))
nrow(inner_join(singles, the_communities, by = c("MLG" = "vertex")))

knitr::kable(singles)
```

>>>>

mcg_mlg_graph
if (!interactive()){
  ggsave(plot = mcg_mlg_graph, filename = file.path(PROJHOME, "results/figures/publication/FigureS2.pdf"), 
       width = 88*3, height = 88*3.5, units = "mm")
}
```

Of interest is accounting for the communities that have a single MLG within the
community. This gives us a lower bound at how many MLGs are reproductively
isolated. We detect these by filtering for communities that only have one MLG:

```{r}
singles <- the_communities %>% 
  mutate(MLG = grepl("MLG", vertex)) %>% 
  group_by(community) %>% 
  summarize(n = sum(MLG)) %>% 
  filter(n == 1) %>%
  inner_join(the_communities, by = "community") %>% 
  mutate(type = case_when(grepl("MLG", vertex) ~ "MLG", TRUE ~ "MCG")) %>% 
  group_by(community, type) %>% 
  summarize(vertex = paste(as.character(vertex), collapse = ", ")) %>%
  spread(type, vertex) 
# assessing that this truely contains the singletons
nrow(inner_join(singles, the_communities, by = c("MLG" = "vertex")))
knitr::kable(singles)
```

### 2017-07-25 doc/manuscript/manuscript.Rmd
update manuscript and calculation of singletons

We wanted to assess if there was correlation between multilocus genotypes (MLG) and mycelial compatibility groups (MCG). 
This was done using a graph-based approach with community analysis.
We first created a contingency table with MLGs and MCGs and converted it to a directed and weighted edgelist where each edge was a connection from an MCG to an MLG weighted by the number of samples shared in the connection. 
The cluster walktrap community detection algorithm as implemented in the `cluster_walktrap()` function in *igraph* version 1.0.1 was used to define clusters of MLGs and MCGs [@csardi2006igraph; @pons2006computing].
All communities that had fewer than 10 members were then consolidated into one.
These community definitions were then used to assess the average genetic distance (as defined by Bruvo's distance) within members of the community [@bruvo2004simple].

@@

Our network-based approach to correlating MLGs with MCGs revealed a large and complex network (Fig. \@ref(biggraph)). 
Community analysis showed 51 communities, 23 of which consisted of a single MLG/MCG pair. 
The three communities with the most members contained 8 of the ten most abundant MCGs. 
Comparing these communities with Bruvo's genetic distance revealed and average distance of 0.451 among communities and an average distance of 0.437 within communities, showing no significant difference.
Overall, there was no clear pattern to the association between MLG and MCGs.

>>>>

We wanted to assess if there was correlation between multilocus genotypes (MLG) and mycelial compatibility groups (MCG). 
This was done using a graph-based approach with community analysis.
We first created a contingency table with MLGs and MCGs and converted it to a directed and weighted edgelist where each edge was a connection from an MCG to an MLG weighted by the number of samples shared in the connection. 
This was then converted to a bipartite graph where top nodes represented MCGs and bottom nodes represented MLGs.
The cluster walktrap community detection algorithm as implemented in the `cluster_walktrap()` function in *igraph* version 1.0.1 was used to define clusters of MLGs and MCGs [@csardi2006igraph; @pons2006computing].
All communities that had fewer than 10 members were then consolidated into one.
These community definitions were then used to assess the average genetic distance (as defined by Bruvo's distance) within members of the community [@bruvo2004simple].

@@

Our network-based approach to correlating MLGs with MCGs revealed a large and complex network (Fig. \@ref(biggraph)). 
Community analysis showed 51 communities, 26 of which consisted of a single MLG indicating that 15.76% of the 165 MLGs are unable to cross with any other MLG in this data set.
The three communities with the most members contained 8 of the ten most abundant MCGs. 
Comparing these communities with Bruvo's genetic distance revealed and average distance of 0.451 among communities and an average distance of 0.437 within communities, showing no significant difference.
Overall, there was no clear pattern to the association between MLG and MCGs.
